### 2024-10-11 draft/wigglyhedra.tex
start FPSAC

\begin{remark}
\label{rem:numberWigglyArcs}
The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell)$.
\end{remark}

@@

\begin{definition}
\label{def:CambrianWigglyPermutations}
A \defn{$\delta$-wiggly permutation} is a wiggly permutation~$\sigma$ of~$[2n]$ such that
% for all~$j \in [n]$, we have~ and~$\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$i \in [2j-2]$.
%\begin{itemize}
%\item $\sigma^{-1}(2j-1) > \sigma^{-1}(2j)$ for all~$j \in [n]$,
%\item $\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$j \in [n]$ and~$i \in [2j-2]$.
%\end{itemize}
\[
\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
\qquad\text{and}\qquad
\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)
\]
%$\delta_j > 0 \implies \sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ and~$\delta_j < 0 \implies \sigma^{-1}(i) \ge \sigma^{-1}(2j)$
for all~$1 \le i \le 2j \le 2n$.
The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly permutation lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
\end{definition}

@@

\begin{definition}
\label{def:wigglyComplexPointSet}
Fix a point set~$P$ of the plane, and an arbitrary total order~$<$ on~$P$.
A \defn{wiggly arc} is a quadruple~$(p,q,R,S)$ where~$p < q \in P$ and the sets~$R$ and~$S$ form a partition of the points of~$P$ located in the open segment joining~$p$ to~$q$.
Two wiggly arcs~$(p,q,R,S)$ and~$(p',q',R',S')$ are \defn{crossing} if 
\begin{itemize}
\item either the segments~$[p,q]$ and~$[p',q']$ cross, 
\item or~$(R \cap S') \cup (\{p,q\} \cap S') \cup (R \cap \{p',q'\}) \ne \varnothing \ne (R' \cap S) \cup (\{p',q'\} \cap S) \cup (R' \cap \{p,q\})$,
\end{itemize}
A set~$X$ of wiggly arcs is \defn{pointed} if for any~$p \in P$, the wiggly arcs of~$X$ with an endpoint at~$p$ generate a pointed cone.
The \defn{wiggly complex}~$\wigglyComplex_P$ is the simplicial complex of pairwise pointed and non-crossing subsets of wiggly arcs.
Note that the boundary wiggly arcs are irrelevant, which allows us to consider a reduced wiggly complex~$\wigglyComplex_P$ induced by internal wiggly arcs.
A \defn{wiggly pseudotriangulation} of~$P$ is a facet of~$\wigglyComplex_P$.
The \defn{wiggly flip graph}~$\wigglyFlipGraph_P$ is the adjacency graph of the facets of~$\wigglyComplex_P$.
%Note that, by construction, $\wigglyFlipGraph_P$ is regular.
See \cref{fig:wigglyComplexSquarre} for an illustration.
%
\begin{figure}[!h]
\centerline{\includegraphics[scale=1]{wigglyComplexSquare}}
\caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of a point set~$P$.}
\label{fig:wigglyComplexSquarre}
\end{figure}
\end{definition}

>>>>

\begin{remark}
\label{rem:numberWigglyArcs}
The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell) = 2^{n+2}-n-3$.
\end{remark}

@@

\begin{definition}
\label{def:CambrianWigglyPermutations}
A \defn{$\delta$-wiggly permutation} is a wiggly permutation~$\sigma$ of~$[2n]$ such that
% for all~$j \in [n]$, we have~ and~$\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$i \in [2j-2]$.
%\begin{itemize}
%\item $\sigma^{-1}(2j-1) > \sigma^{-1}(2j)$ for all~$j \in [n]$,
%\item $\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$j \in [n]$ and~$i \in [2j-2]$.
%\end{itemize}
\[
\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
\qquad\text{and}\qquad
\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)
\]
%$\delta_j > 0 \implies \sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ and~$\delta_j < 0 \implies \sigma^{-1}(i) \ge \sigma^{-1}(2j)$
for all~$1 \le i \le 2j \le 2n$.
The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
\end{definition}

@@

\begin{definition}
\label{def:wigglyComplexPointSet}
Fix a point set~$P$ of the plane, and an arbitrary total order~$<$ on~$P$.
A \defn{wiggly arc} is a quadruple~$(p,q,R,S)$ where~$p < q \in P$ and the sets~$R$ and~$S$ form a partition of the points of~$P$ located in the open segment joining~$p$ to~$q$.
Two wiggly arcs~$(p,q,R,S)$ and~$(p',q',R',S')$ are \defn{crossing} if 
\begin{itemize}
\item either the segments~$[p,q]$ and~$[p',q']$ cross, 
\item or~$(R \cap S') \cup (\{p,q\} \cap S') \cup (R \cap \{p',q'\}) \ne \varnothing \ne (R' \cap S) \cup (\{p',q'\} \cap S) \cup (R' \cap \{p,q\})$.
\end{itemize}
A set~$X$ of wiggly arcs is \defn{pointed} if for any~$p \in P$, the wiggly arcs of~$X$ with an endpoint at~$p$ generate a pointed cone.
The \defn{wiggly complex}~$\wigglyComplex_P$ is the simplicial complex of pairwise pointed and non-crossing subsets of wiggly arcs.
Note that the boundary wiggly arcs are irrelevant, which allows us to consider a reduced wiggly complex~$\wigglyComplex_P$ induced by internal wiggly arcs.
A \defn{wiggly pseudotriangulation} of~$P$ is a facet of~$\wigglyComplex_P$.
The \defn{wiggly flip graph}~$\wigglyFlipGraph_P$ is the adjacency graph of the facets of~$\wigglyComplex_P$.
%Note that, by construction, $\wigglyFlipGraph_P$ is regular.
See \cref{fig:wigglyComplexSquarre} for an illustration.
%
\begin{figure}[!h]
\centerline{\includegraphics[scale=1]{wigglyComplexSquare}}
\caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of a point set~$P$.}
\label{fig:wigglyComplexSquarre}
\end{figure}
\end{definition}

### 2024-10-11 exposeBerlin2410/exposeBerlin2410.tex
start FPSAC

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\  \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ \\  \end{tabular}

@@

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\ triangles \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\ pseudotriangles \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ $k$-stars \\ \papier{P.--Santos ('09)} \end{tabular}

@@

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
\hspace{1.5cm} associahedron \hspace{2.6cm} pseudotriangulation polytope \hspace{1.2cm} multiassociahedron

@@

\begin{slide}{LINE SPACE OF THE PLANE = M\"OBIUS STRIP}

\centerline{\includegraphics[angle=-90,scale=2]{MoebiusBand}}

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

@@

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures6}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

@@

\vspace{.1cm}
\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\vspace{.5cm}
\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\hfill \papier{Bapat--P. (24$^+$)}
}

@@

\hfill \papier{Bapat--P. (24$^+$)}
}
\end{minipage}

@@

\vspace{.5cm}
\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases. \hfill \papier{Bapat--P. (24$^+$)}}

@@

\vspace{.1cm}
\theo{THM}{The cones~$\setangle{\b{g}(\alpha)}{\alpha \in D}$ for all wiggly dissections~$D$ form a complete simplicial fan~$\wigglyFan_n$ (in $\sum_{i = 1}^{2n} x_i = 0$). \hfill \papier{Bapat--P. (24$^+$)}
}

@@

\vspace{-.6cm}
\hfill \papier{Bapat--P. (24$^+$)}
}

@@

\vspace{-.5cm}
\hfill \papier{Bapat--P. (24$^+$)}
}

@@

\hfill \color{gray}{[NB: wiggly permutations do not form a zigzag language, right?]}
}

>>>>

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\  \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter ('96)} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ \\  \end{tabular}

@@

\hspace{1.7cm} 
\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\ triangles \end{tabular} 
\hspace{3.4cm} 
\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter ('96)} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\ pseudotriangles \end{tabular}
\hspace{2cm} 
\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ $k$-stars \\ \papier{P.--Santos ('09)} \end{tabular}

@@

\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
\hspace{1.5cm} associahedron \hspace{2.4cm} \begin{tabular}[t]{c}pseudotriangulation polytope \\  \papier{Rote--Santos--Streinu ('03)} \end{tabular} \hspace{1cm} multiassociahedron

@@

%\begin{slide}{LINE SPACE OF THE PLANE = M\"OBIUS STRIP}
%
%\centerline{\includegraphics[angle=-90,scale=2]{MoebiusBand}}
%
%\end{slide}
%
%%%%%%%%
%
%\multido{\n=0+1}{10}{%
%\begin{slide}{Duality}
%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
%\vspace{-.5cm}\\
%\vspace*{-2cm}
%\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
%\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
%\end{slide}
%}
%
%%%%

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$

@@

\begin{slide}{Duality}
\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures6}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$

%%%%
%
%\multido{\n=0+1}{10}{%
%\begin{slide}{Duality}
%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
%\vspace{-.5cm}\\
%\vspace*{-2cm}
%\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
%\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
%\end{slide}
%}
%
%%%%

@@

\vspace{.1cm}
\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells. \hfill \papier{Bapat--P. (24$^+$)}

@@

\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed. \hfill \papier{Bapat--P. (24$^+$)}

@@

\vspace{.5cm}
\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected. \hfill \papier{Bapat--P. (24$^+$)}

@@

\hfill \papier{Bapat--P. (24$^+$)}

@@

\hfill \papier{Bapat--P. (24$^+$)}

}
\end{minipage}

@@

\vspace{.5cm}
\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases. \hfill \papier{Bapat--P. (24$^+$)}

@@

\vspace{.1cm}
\theo{THM}{The cones~$\setangle{\b{g}(\alpha)}{\alpha \in D}$ for all wiggly dissections~$D$ form a complete simplicial fan~$\wigglyFan_n$ (in $\sum_{i = 1}^{2n} x_i = 0$). \hfill \papier{Bapat--P. (24$^+$)}

@@

\vspace{-.6cm}
\hfill \papier{Bapat--P. (24$^+$)}

@@

\vspace{-.5cm}
\hfill \papier{Bapat--P. (24$^+$)}

@@

\hfill \color{gray}{[NB: wiggly permutations do not form a zigzag language]}
}
